### 2017-07-13 pkg/model4you/inst/JORS/man_model4you.Rnw
reuse potential
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1505 255f4249-2263-4417-b1ea-8498779e27a7

\section*{Quality control}

Tests, code in this manual, examples in documentation

@@

The software is intentionally written to make usage as simple as possible. We
hope that researchers use it for analysis of:
\begin{itemize}
\item Clinical trials
\item A-B testing
\item Other situations where the comparison of two decisions is of interest
\end{itemize}
We encourage users to use the partykit forum on R-forge
(\url{https://r-forge.r-project.org/forum/forum.php?forum_id=852}) or the party
tag on Stackoverflow (\url{http://stackoverflow.com/questions/tagged/party}) in
case of questions or problems.

>>>>

\section*{Quality control}
All packages on CRAN undergo standard checks for compatibility with the R
package ecosystem.  The R package contains examples and tests. These were run
and checked on Linux 86\_64 and Windows.

@@

The software is intentionally written to make usage as simple as possible. The
most prominent use case are clinical trials where the assumption of an average
treatment effect for all patients is too strict and the efficacy of the
treatment depends on patient characteristics (e.g. gender, biomarkers, etc.).
For subgroup analyses (stratified treatment effects) model-based trees
(\Sexpr{'pmtree()'}) can be used; For personalised treatment effects
model-based forests (\Sexpr{'pmforest()'}) provide a way of estimating
similarity between patients and using this similarity measure to estimate
personalised models (\Sexpr{'pmodel()'}).  The target audience are people who
deal with heterogeneous treatment effects, such as medical researchers,
pharmaceutical companies or analysts in marketing (A-B testing).  In general
the software is useful to researchers dealing with scenarios where two
exposures are compared and responses of subjects possibly depend on other
variables.

We encourage users to use the party tag on Stackoverflow
(\url{http://stackoverflow.com/questions/tagged/party}) in case of questions or
problems.
